Characterizing subarctic biomes for land surface modeling of pollution and climate risk

### 2021-05-10 VegOzone.tex
Fix broken hyperkink
Write about modis retrieved start and end of greening season.

\section{DO3SE modeling}
\label{sec:do3se}
To investigate the difference between 2018 and 2019 concerning stomatal ozone uptake and to assess which of the environmental factors might be most influential in determining \chem{O_3} damage risk, we model ozone uptake of different natural and semi-natural vegetation using the $\mathrm{DO_3SE}$ model and develop bespoke subarctic parameterizations for common plant species. We the $\mathrm{DO_3SE}$ model and gapp-filling methods are described in Appendix~\ref{sec}. First, we give an account of the methodology for deriving bespoke parameters. Then, we will present and discuss the modeling results.

@@

\begin{figure*}[t]
  \includegraphics[width=12cm]{figA3}
  \caption{Reconstruction of missing \chem{[O_3]} observation data at Svanvik in July 2018 based on derived hourly climatologies of northern Fennoscandia, Svanvik, and data Pallas. (a) Time series; (b) anomalies; (c) reconstruction.}
  \label{fig:ozone_reconstruction_2018_07}
\end{figure*}

@@

\begin{figure}[t]
  \includegraphics[width=8.3cm]{figB1}
  \caption{Estimated begin (BGS) and end (EGS) of growing season for coniferous trees from MODIS Aqua/Terra net photosynthesis (PSN) product. A $1\times 1\,\unit{km}$ area around Svanhovd was selected. Daily averaged data for both 2018 and 2019 has been fitted with a quadratic polynomial function. The numerically computed root yields: BGS 122/106 day of year (\unit{doy}) and EGS 261/274 day of year for 2018/2019, respectively.}
  \label{fig:modis_Psn}
\end{figure}

>>>>

\section{DO3SE modeling}
\label{sec:do3se}
To investigate the difference between 2018 and 2019 concerning stomatal ozone uptake and to assess which of the environmental factors might be most influential in determining \chem{O_3} damage risk, we model ozone uptake of different natural and semi-natural vegetation using the $\mathrm{DO_3SE}$ model and develop bespoke subarctic parameterizations for common plant species. We the $\mathrm{DO_3SE}$ model and gapp-filling methods are described in Appendix~\ref{appendix:do3se_model}. First, we give an account of the methodology for deriving bespoke parameters. Then, we will present and discuss the modeling results.

@@

%\begin{figure*}[t]
%  \includegraphics[width=12cm]{figA3}
%  \caption{Reconstruction of missing \chem{[O_3]} observation data at Svanvik in July 2018 based on derived hourly climatologies of northern Fennoscandia, Svanvik, and data Pallas. (a) Time series; (b) anomalies; (c) reconstruction.}
%  \label{fig:ozone_reconstruction_2018_07}
%\end{figure*}

@@

To assess the $G_\mathrm{start}$  and $G_\mathrm{end}$ of the greening season for coniferous trees at Svanhovd in 2018/19, we used the net photosynthesis product ($A_\mathrm{net}$) of MODIS AQUA/TERRA over a $1\times 1\,\unit{km}$ area centered at Svanhovd. MODIS data indicate a higher photosynthetic activity in 2018 than in 2019. As shown in Fig.~\ref{fig:modis_Psn} we fitted a second order polynomal function of the general form
%
\begin{equation}
A_\mathrm{net}(t) =  -m_0\cdot(t-m_1)^2+m_2,
\end{equation}
%
with the form parameters $m_i$ through the data. Numerically, we retrieved the roots as $G_\mathrm{start}$ 122/106 and $G_\mathrm{end}$ 261/274 for 2018 and 2019, respectively.

\begin{figure}[t]
  \includegraphics[width=8.3cm]{figB1}
  \caption{Estimated $G_\mathrm{start}$ and $G_\mathrm{end}$ of growing season for coniferous trees from MODIS Aqua/Terra net photosynthesis (PSN) product. A $1\times 1\,\unit{km}$ area around Svanhovd was selected. Daily averaged data for both 2018 and 2019 has been fitted with a quadratic polynomial function. The numerically computed root yields: BGS 122/106 day of year (\unit{doy}) and EGS 261/274 day of year for 2018/2019, respectively.}
  \label{fig:modis_Psn}
\end{figure}
